---
title: "Data_Transformation_Part2"
author: "DA101"
date: "2025-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
#Import the tidyverse package and nycflights13
install.packages("tidyverse")
library(tidyverse)

install.packages("nycflights13")
library(nycflights13)
```

```{r}
#Import the dataset flights
data(flights)

```

Besides selecting sets of existing columns, it’s often useful to add new columns that are functions of existing columns. That’s the job of mutate().

mutate() always adds new columns at the end of your dataset so we’ll start by creating a narrower dataset so we can see the new variables. Remember that when you’re in RStudio, the easiest way to see all the columns is View().

```{r}
#create a new dataset called flights_sml by selecting columns month, day, dep_delay, arr_delay, distance, and air_time


```


```{r}
#use mutate() to create a new column gain (dep_delay - arr_delay) and speed (distance/air_time * 60)

```

Use the pipe, %>%, to write multiple operations in one line of code
```{r}
#Calculate the mean distance and mean arrival delay grouped by destination

```

Use $ to select a specific column in the dataset flights
```{r}
#Find the average of dep_delay

```
The average of dep_delay is NA because there are missing values in the column. To count the number of missing values, use sum(is.na(x)).
```{r}
#Count the number of missing values in the column dep_delay. Use flights$dep_delay to select the column


```
To remove the NAs from our calculation, add na.rm = TRUE
```{r}


```
To count the number of distinct (unique) values, use n_distinct(x).
```{r}
#Which destinations have the most carreirs?

```
