---
title: "Importing Data"
author: "DA101"
date: "2025-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("tidyverse")
library(tidyverse)

install.packages("dplyr")
library(dplyr)
```


```{r}
#import file called students.csv

```


```{r}
#view students

```

In the favourite.food column, there are a bunch of food items, and then the character string N/A, which should have been a real NA that R will recognize as “not available”. This is something we can address using the na argument. By default, read_csv() only recognizes empty strings ("") in this dataset as NAs, and we want it to also recognize the character string "N/A".
```{r}
#replace character "N/A" in favourite.food with a missing value

```


```{r}
#view students

```


```{r}
#check class of column mealPlan


```

Since meal_plan is a categorical variable with a known set of possible values, which in R should be represented as a factor:
```{r}
#change mealPlan from character class to a factor class


```


```{r}
#change five to 5 in column AGE

```
