---
title: "R_Programming_Basics"
author: "DA101"
date: "2025-02-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Ok, let's get started.

```{r}
#assign 5 + 7 to x 
x <- 5+7

#print the value of x
print(x)

```

```{r}
#assign 8-4 to y
y <- 8-4

#print the value of y
print(y)

```

```{r}
#create variable w by multiplying x and y
w <- x * y

#print the value of w
print(w)

```

**vectors**

Now, let's create a small collection of numbers called a vector. Any object that contains data is called a data structure and numeric vectors are the simplest type of data structure in R. In fact, even a single number is considered a vector of length one.

The easiest way to create a vector is with the c() function, which stands for 'concatenate' or 'combine'. To create a vector containing the numbers 1.1, 9, and 3.14, type c(1.1, 9, 3.14). Try it now and store the result in a variable called z.

```{r}
#Make a vector containing the numbers 1.1, 9, and 3.14. Save the result in a variable z.  
z <- c(1.1, 9, 3.14)


#Then print the contents of z.
print(z)

```

Numeric vectors can be used in arithmetic expressions. Run the following to see what happens: z * 2 + 100.

You code here:

```{r}
z
z*2 + 100

```

Hopefully you got the following output

[1] 102.20 118.00 106.28

First, R multiplied each of the three elements in z by 2. Then it added 100 to each element to get the result you see above.

This illustrates the vectorization concept in R.  Many operations or functions, when applied to a vector, are applied to each element of the vector.

Other common arithmetic operators are `+`, `-`, `/`, and `^` (where x^2 means 'x squared'). To take the square root, use the sqrt() function and to take the absolute value, use the abs() function.

Take the square root of z - 1 and assign it to a new variable called my_sqrt.

```{r}
#your code here
my_sqrt <- sqrt(z-1)

```

Before you view the contents of the my_sqrt variable, what do you think it contains?

1: a vector of length 3
2: a single number (i.e a vector of length 1)
3: a vector of length 0 (i.e. an empty vector)

Now find out

```{r}
#display the contents of my_sqrt
print(my_sqrt)

#check the class of my_sqrt using class()
class(my_sqrt)
```

Now, create a new variable called my_div that gets the value of z divided by my_sqrt.

and display the contents of my_div

```{r}
#create my_div
my_div <- z/my_sqrt

#print my_div
print(my_div)

```
Hopefully it looks something like this
[1] 3.478505 3.181981 2.146460

